Note on Linear Biases in MORUS

### 2018-04-11 morus.tex
fixed mistake in alphabetic ordering of authors (apologies to Yu)

\ifanonymous
\author{}
\institute{}
\else
\author{Tomer Ashur, Maria Eichlseder, Ga\"etan Leurent,\\Brice Minaud, Yann Rotella, Beno\^it Viguier, Yu Sasaki}
\institute{}
%\path|tomer.ashur@esat.kuleuven.be|, \path|maria.eichlseder@iaik.tugraz.at|, \path|gaetan.leurent@inria.fr|, \path|brice.minaud@gmail.com|, \path|yann.rotella@inria.fr|, \path|b.viguier@science.ru.nl|, \path|sasaki.yu@lab.ntt.co.jp|
\fi

@@

In the actual trail for (either version of) full \cipher{MORUS}, this exact situation occurs when combining trail fragments $\beta^t_i$ and $\gamma^t_i$. Indeed, $\beta^t_i$ requires approximating the term $S^t_{2,i} \cdot S^t_{3,i}$, while $\gamma^t_i$ requires approximating the term $S^t_{2,i} \cdot S^t_{3,i-w}$ (cf. \Cref{fig:trailcollision}). While in \cipher{MiniMORUS}, these terms cancel out, in the full \cipher{MORUS}, when adding all symmetric copies of the trail, we end up with the sum:
\begin{align}
&S^t_{2,i} \cdot S^t_{3,i} \oplus S^t_{3,i} \cdot S^t_{2,i+w}
\oplus S^t_{2,i+w} \cdot S^t_{3,i+w} \oplus S^t_{3,i+w} \cdot S^t_{2,i+2w}\notag\\
\oplus\; &S^t_{2,i+2w} \cdot S^t_{3,i+2w} \oplus S^t_{3,i+2w} \cdot S^t_{2,i+3w}
\oplus S^t_{2,i+3w} \cdot S^t_{3,i+3w} \oplus S^t_{3,i+3w} \cdot S^t_{2,i}.\label{eq:8circle}
\end{align}
It may be observed that the products occurring in the equation above involve 8 terms in a ring. The weight of this expression can be computed by brute force, and is equal to $3$.

>>>>

\ifanonymous
\author{}
\institute{}
\else
\author{Tomer Ashur, Maria Eichlseder, Ga\"etan Leurent,\\Brice Minaud, Yann Rotella, Yu Sasaki, Beno\^it Viguier}
\institute{}
%\path|tomer.ashur@esat.kuleuven.be|, \path|maria.eichlseder@iaik.tugraz.at|, \path|gaetan.leurent@inria.fr|, \path|brice.minaud@gmail.com|, \path|yann.rotella@inria.fr|, \path|b.viguier@science.ru.nl|, \path|sasaki.yu@lab.ntt.co.jp|
\fi

@@

In the actual trail for (either version of) full \cipher{MORUS}, this exact situation occurs when combining trail fragments $\beta^t_i$ and $\gamma^t_i$. Indeed, $\beta^t_i$ requires approximating the term $S^t_{2,i} \cdot S^t_{3,i}$, while $\gamma^t_i$ requires approximating the term $S^t_{2,i} \cdot S^t_{3,i-w}$ (cf. \Cref{fig:trailcollision}). While in \cipher{MiniMORUS}, these terms cancel out, in the full \cipher{MORUS}, when adding all symmetric copies of the trail, we end up with the sum:
\begin{align}
&S^t_{2,i} \cdot S^t_{3,i} \oplus S^t_{3,i} \cdot S^t_{2,i+w}
\oplus S^t_{2,i+w} \cdot S^t_{3,i+w} \oplus S^t_{3,i+w} \cdot S^t_{2,i+2w}\notag\\
\oplus\; &S^t_{2,i+2w} \cdot S^t_{3,i+2w} \oplus S^t_{3,i+2w} \cdot S^t_{2,i+3w}
\oplus S^t_{2,i+3w} \cdot S^t_{3,i+3w} \oplus S^t_{3,i+3w} \cdot S^t_{2,i}.\label{eq:8circle}
\end{align}
It may be observed that the products occurring in the equation above involve eight terms forming a ring. The weight of this expression can be computed by brute force, and is equal to $3$.
